Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2020-02-04 Tex/Old text/chapters/conclusion.tex
thesis update

The first contribution was presented in ~\autoref{chap:automatedverification}, we described and evaluated an automated verification method of validating a given stand-alone PV system. Our method, using model checking, can perform a size check and verify, over time, whether a PV system meets electrical requirements. We showed that there are various possible ways to perform that validation, such as testing, laboratory measuring, or even simulation. However, we developed an algorithm and a tool using model checking that was feasible and effective. Our results were supported by case studies, by data gathered from the field, and by interviews with PV owners.

@@

%In a nutshell, our proposed PV system validation method, who check the size of inputted PV system, and verifies it over the time, was feasible and effective, supported by a algorithm written to implement the method, by a comparative with a commercial simulation tool, and by real data collect at the field.
%
In the comparison among verification engines, ESBMC with the SMT solver Z3 executed in the ``incremental SMT'' configuration presented a better performance than CBMC (around four times faster), used less RAM than CBMC and CPAchecker (less than $2$ GB when compared to $9.2$ GB for CBMC and 19.2GB for CPAchecker). All our experimental results are sound since the PV owners and the monitoring system validated the possible flaws that the system could present in the field.
%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.

>>>>

The first contribution was presented in ~\autoref{chap:automatedverification}, we described and evaluated an automated verification method of validating a given stand-alone PV system. Our method, using model checking, can perform a size check and verify, over time, whether a PV system meets electrical requirements. There are various possible ways to perform that validation, such as testing, laboratory measuring, or even simulation. However, we developed an algorithm and a tool using model checking that is feasible and effective. Our results were supported by case studies, by data gathered from the field, and by interviews with PV owners.

@@

%In a nutshell, our proposed PV system validation method, who check the size of inputted PV system, and verifies it over the time, was feasible and effective, supported by a algorithm written to implement the method, by a comparative with a commercial simulation tool, and by real data collect at the field.
%
In the comparison among verification engines, ESBMC with the SMT solver Z3 executed in the ``incremental SMT'' configuration presented a better performance than CBMC (around four times faster), used less RAM than CBMC and CPAchecker (less than $2$ GB when compared to $9.2$ GB for CBMC and 19.2GB for CPAchecker) as expected and explained in Section~\ref{sec:ESBMC}. All our experimental results are sound since the PV owners and the monitoring system validated the possible flaws that the system could present in the field.
%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.

### 2020-02-04 Tex/Old text/chapters/introduction.tex
thesis update

Nothing more than a niche market only a few years ago, solar PV systems have become a mainstream electricity provider, with an  approximate 50\% increase (or 100.9 GW)in new PV installations from 2016 to 2017~\cite{EPIA}, although this growth is not driven by stand-alone systems.

However, in order to provide universal electricity, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed. Grid extension will be the standard, especially in urban areas~\cite{IEAweo2018}.

@@

Simply put, we aim to present new techniques that will ensure that you have good designs of stand-alone solar PV systems, that do not cause a drop in energy supply, and that these systems are designed at the lowest possible cost.

>>>>

Nothing more than a niche market only a few years ago, solar PV systems have become a mainstream electricity provider, with an  approximate 50\% increase (or 100.9 GW)in new PV installations from 2016 to 2017~\cite{EPIA}, although this growth is not driven by stand-alone systems. However, in order to provide universal electricity, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed. Grid extension will be the standard, especially in urban areas~\cite{IEAweo2018}.

@@

\textbf{Simply put, we aim to present new techniques that will guarantee a good design of stand-alone solar PV systems, that do not cause a drop in energy supply after deployment, and that these systems are designed at the lowest possible cost.}
